??

### 2018-06-12 manuscript/main.tex
Create the figure on vbsr

\begin{figure*}[htb!]
\centering
\includegraphics[width=\textwidth]{Figures/clustering}
\caption{\textbf{Consensus clustering of methylation probes for \citet{figueroa2010dna}} (a) consensus matrix for k = $6, 7, 8$. $k = 7$ shows high intra-cluster consensus and low intercluster consensus. (b) cumulative distribution function of consensus matrix at each $k = 1, \dots, 10$. $k = 7$ approaches the maximum consensus distribution (c) Area under CDF of consensus matrix for $k = 1, \dots, 10$. $k = 7$ is the largest $k$ with a appreciable increase in consensus (d) Hierarchical clustering of cases and probes. Each row represents a probe and each column represents a patients. Methylation intensity level were row and column normalized. The16 clusters of AML cases from \citet{figueroa2010dna} were reproduced. Probes were clustered using Ward's method with Pearson correlation distance transformed to Euclidean space and $k=7$ were chosen as the cutoff from CC.}
\label{CC}
\end{figure*}

@@

Figure \ref{CC} shows the results of consensus clustering on probes and significantly enriched biological processes in each cluster is shown below in Table \ref{enriched}.

@@

>>>>

\begin{figure*}[htb!]
\centering
\includegraphics[width=\textwidth]{Figures/clustering}
\caption{\textbf{Consensus clustering of methylation probes for \citet{figueroa2010dna}} (a) consensus matrix for k = $6, 7, 8$ (b) cumulative distribution function of consensus matrix at each $k = 1, \dots, 10$ (c) Area under CDF of consensus matrix for $k = 1, \dots, 10$ (d) Hierarchical clustering of cases and probes. Each row represents a probe and each column represents a patients. Methylation intensity level were row and column normalized. The16 AML cases from \citet{figueroa2010dna} were reproduced. Probes were clustered using Ward's method with lingoes transformation of 1 - Pearson correlation distance transformed to Euclidean space and $k=7$ were chosen as the cutoff from CC.}
\label{CC}
\end{figure*}

@@

Figure \ref{CC} shows the results of consensus clustering on probes. [Explain the choice of 7 clusters]
 $k = 7$ shows high intra-cluster consensus and low intercluster consensus.
$k = 7$ approaches the maximum consensus distribution 
$k = 7$ is the largest $k$ with a appreciable increase in consensus 
 and significantly enriched biological processes in each cluster is shown below in Table \ref{enriched}.

@@

\subsection{vBsr}

\begin{figure*}[htb!]
\includegraphics[width=\textwidth]{Figures/vBsr}
\caption{\textbf{Heatmap of methylation clusters, average methylation level and gene expression probes significantly associate with average methylation level}}
\end{figure*}
